### 2014-10-21 paper/include/dtail.tex
durr

When a row is selected for refresh by the memory controller, DTail intercepts the refresh command and based on the Retention Time and Validity information either lets the refresh to be performed or cancels it. The method used for refreshing a row depends on what is the most efficient at the time, if a large number of rows need refresh then CBR is selected, otherwise ROR is used.

>>>>

When a row is selected for refresh by the memory controller, DTail intercepts the refresh command and based on the Retention Time and Validity information either lets the refresh to be performed or cancels it. The command used for refreshing a row depends on what is the most efficient at the time, if a large number of rows need refresh then CBR is selected, otherwise ROR is used.
